DraftFunctions

### 2021-05-21 R/DraftFunctions.Rmd
addtreedim function writing

# Data loading
```{r}
data(Paracou6_2016) #data inventory in the global environment
data("ForestZoneVolumeParametersTable") # The volume parameters data in the global environment
load(system.file("extdata", "BrokenParacou6_2016.rda", package = "Maria")) # the test inventory in the global environment
load(system.file("extdata", "ParamCrownDiameterAllometry.rda", package = "Maria"))
```
```{r}
lapply(Paracou6_2016, class) #give the class of all the data variables
```

@@

```{r TreeHeight}
library(BIOMASS)
library(knitr)
if (!("DBH" %in% names(Paracou6_2016))) {add_column(Paracou6_2016, DBH = NA) #if DBH (cm) doesn't exist create it
  Paracou6_2016$DBH = Paracou6_2016$CircCorr/pi} # and compute it
# TreeHeight = hauteur de l’arbre (H) (en mètre) (BIOMASS package)
# 3 options :
# - get my tree heights from the location (from continent or region specific model, or from coordinates)
# - from other Guyanese trees heights data, fit different H-D models, select the best and apply on my data.

RegionTreeHeight <- retrieveH(D = Paracou6_2016$DBH, region = "GuianaShield") #continent or region specific model (Feldpaush et al. (2012))
# GuianaShield = Guyana, French Guiana (piste St Elie (Chave 2005)), Venezuela

n <- length(Paracou6_2016$CircCor)
coord <- cbind(long = rep(-52.92, n), lat = rep(5.27, n)) # Paracou P6 coordinates
CoordTreeHeight <- retrieveH(D = Paracou6_2016$DBH, coord = coord) #by coordinates (Chave et al. (2012))

# Just with Nouragues data (measurement: laser rangefinder):
ModelsresultNouraguesdata <- modelHD(
  D = NouraguesHD$D,
  H = NouraguesHD$H,
  useWeight = TRUE
)
kable(ModelsresultNouraguesdata) #log2 has the lowest RSE (4.222718) (Root Squared Error)
HDmodelNouraguesdata <- modelHD(
  D = NouraguesHD$D,
  H = NouraguesHD$H,
  method = "log2", # Compute the local H-D model with the lowest RSE.
  useWeight = TRUE
)
TreeHeightEstimation <- retrieveH(
  D = Paracou6_2016$DBH,
  model = HDmodelNouraguesdata
)
## Put these tree heights estimations in the inventory
Paracou6_2016TreeHeight <- Paracou6_2016 %>% 
  mutate(TreeHeight = TreeHeightEstimation$H)
plot(Paracou6_2016TreeHeight$DBH, Paracou6_2016TreeHeight$TreeHeight)#amazing !! It's a log2 form

@@

unique(Paracou6_2016_crown[(Paracou6_2016_crown$Taxo == "mean"),]$ScientificName) #which species are no recognized
length(unique(Paracou6_2016_crown$ScientificName)) #How many species are in the plot
```
#' @examples
#' data(Paracou6_2016)
#' if (!("DBH" %in% names(inventory))) {add_column(inventory, DBH = NA) #if DBH doesn't exist create it
#' inventory$DBH = inventory$CircCorr/pi} # and compute it
#' cleaninventory(inventory = Paracou6_2016)

@@

  # CrownDiameter (m)
  unite(Genus, Species, col = "ScientificName", sep = "_", remove = F) %>% 
  left_join(spParamCrownDiameter, by = c("ScientificName","Genus","Species")) %>% #Add parameters at species scale
  left_join(genParamCrownDiameter, by = "Genus", suffix = c(".species", ".genus")) %>% #Add parameters at genus scale
  left_join(famParamCrownDiameter, by = "Family") %>% #Add parameters at family scale

>>>>

# Data loading
```{r}
data(Paracou6_2016) #data inventory in the global environment
data("ForestZoneVolumeParametersTable") # The volume parameters data in the global environment
# load(system.file("extdata", "BrokenParacou6_2016.rda", package = "Maria")) # the test inventory in the global environment
load(system.file("extdata", "ParamCrownDiameterAllometry.rda", package = "Maria"))
```
```{r}
lapply(Paracou6_2016, class) #give the class of all the data variables
```

@@

```{r TreeHeight}
library(BIOMASS)
library(knitr)

#if DBH (cm) doesn't exist create it
if (!("DBH" %in% names(Paracou6_2016))) {add_column(Paracou6_2016, DBH = NA)
  Paracou6_2016$DBH = Paracou6_2016$CircCorr/pi} # and compute it

# TreeHeight = hauteur de l’arbre (H) (en mètre) (BIOMASS package)
# 3 options :
# - get my tree heights from the location (from continent or region specific model, or from coordinates)
# - from other Guyanese trees heights data, fit different H-D models, select the best and apply on my data.

#continent or region specific model (Feldpaush et al. (2012))
RegionTreeHeight <- retrieveH(D = Paracou6_2016$DBH, region = "GuianaShield") # GuianaShield = Guyana, French Guiana (piste St Elie (Chave 2005)), Venezuela

#by coordinates (Chave et al. (2012))
n <- length(Paracou6_2016$CircCor)
coord <- cbind(long = rep(-52.92, n), lat = rep(5.27, n)) # Paracou P6 coordinates
CoordTreeHeight <- retrieveH(D = Paracou6_2016$DBH, coord = coord)

# Just with Nouragues data (measurement: laser rangefinder):
# Fit first different height-diameter models
ModelsresultNouraguesdata <- modelHD( # modelHD = .
  D = NouraguesHD$D,
  H = NouraguesHD$H,
  useWeight = TRUE # model weights will be (D^2)*H (weights are proportional to tree volume, so that larger trees have a stronger influence during the construction of the model)
)
# choose the best model
kable(ModelsresultNouraguesdata) #log2 has the lowest RSE (4.222718) (Root Squared Error)
HDmodelNouraguesdata <- modelHD(
  D = NouraguesHD$D,
  H = NouraguesHD$H,
  method = "log2", # Compute the local H-D model with the lowest RSE.
  useWeight = TRUE
)
# Applicate the model to retrieve tree heights ---- HERE
TreeHeightEstimation <- retrieveH(
  D = Paracou6_2016$DBH,
  model = HDmodelNouraguesdata
)
## Put these tree heights estimations in the inventory
Paracou6_2016TreeHeight <- Paracou6_2016 %>% 
  mutate(TreeHeight = TreeHeightEstimation$H)
plot(Paracou6_2016TreeHeight$DBH, Paracou6_2016TreeHeight$TreeHeight)#amazing !! It's a log2 form

@@

unique(Paracou6_2016_crown[(Paracou6_2016_crown$Taxo == "mean"),]$ScientificName) #which species are no recognized
length(unique(Paracou6_2016_crown$ScientificName)) #How many species are in the plot
```

@@

  # CrownDiameter (m)
  # Add crown diameter parameters at the inventory:
  unite(Genus, Species, col = "ScientificName", sep = "_", remove = F) %>% 
  left_join(spParamCrownDiameter, by = c("ScientificName","Genus","Species")) %>% #Add parameters at species scale
  left_join(genParamCrownDiameter, by = "Genus", suffix = c(".species", ".genus")) %>% #Add parameters at genus scale
  left_join(famParamCrownDiameter, by = "Family") %>% #Add parameters at family scale
